Pure Spin Current Injection in Hydrogenated Graphene Structures

### 2017-04-26 mu/article/article.tex
tarting V^a description for Up.

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
    structure. The maximum response zone is localized for an energy range from
    0.90\,eV to 0.93\,eV and for a polarization angle of the
    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-vab-mag}
\end{figure}

@@

For the \emph{alt} structure we analyzed the energy range of energy from
0.6\,eV to 1.0\,eV where we found the most intense response for
$\mathcal{V}^{\mathrm{ab}}$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
\ref{fig:alt-vab-mag} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra
resulting from evaluate Eq. \eqref{eq:va-mag} using different polarization
angles $\alpha$ in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We
can see that the onset of the response is when the energy of the incoming light
is the same of the gap energy.

@@

$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. Also there is
another zone of interest for energies from 0.70\,eV to 0.74\,eV where a local
maximum is obtained.
From Fig. \ref{fig:alt-3d-vx} we have that $|\mathcal{V}^{\mathrm{x}}|$reaches
values of 30\,Km/s for the first zone mentioned before and 20\,Km/s for
the second one. 

@@

polarization angle is $\alpha = 145^{\circ}$. 
In the top frames of Figs. \ref{fig:alt-vx-comp-rtp}  and 
\ref{fig:alt-vy-comp-rtp} we present the results for
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing the

@@

energy and the corresponding azimuthal $\theta$ and polar $\varphi$ angles.

@@

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-vab-mag-1}
\end{figure}
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The local maximum response zone is localized for an energy range
    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
    from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-vab-mag-2}
\end{figure}

\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-1}
\end{figure}
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
    \caption{Intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-2}
\end{figure}

>>>>

% %%%%%%%%%%%%%%%%%
% %% Description of ALT |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %% alt-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vx}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vxb}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{alt} structure 
    \label{fig:alt-3d-vy}]
    {\includegraphics[width=\linewidth]{altplots/alt-3d-vyb}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-alt
    structure. The maximum response zone is localized for an energy range from
    0.90\,eV to 0.93\,eV and for a polarization angle of the
    incoming beam from 120$^{\circ}$ to 150$^{\circ}$.}
    \label{fig:alt-3d}
\end{figure}

@@

For the \emph{alt} structure we analyzed the energy range from 0.6\,eV to
1.0\,eV where we found the most intense response for
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{a}}|$. In Fig. 
\ref{fig:alt-3d} we present the $|\mathcal{V}^{\mathrm{a}}|$ spectra resulting 
from evaluate Eq. \eqref{eq:va-mag} using different polarization angles $\alpha$
in Eq. \eqref{eq:vab} for the C$_{16}$H$_{8}$-alt structure. We can see that the
onset of the response is when the energy of the incoming light is the same of
the gap energy.

@@

$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. 
\textcolor{red}{
Also there is another zone of interest for energies from 0.70\,eV to 0.74\,eV
and same polarization angles range where a local maximum is obtained. From Figs.
\ref{fig:alt-3d-vx} and \ref{fig:alt-3d-vy} we have that
$|\mathcal{V}^{\mathrm{x}}|$ reaches values of 30\,Km/s and 20\,Km/s,
respectively.
}

@@

polarization angle is $\alpha = 145^{\circ}$. In the top frames of Figs.
\ref{fig:alt-vx-comp-rtp}  and \ref{fig:alt-vy-comp-rtp} we present the results
for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing the

@@

energy and the corresponding polar $\varphi$ and azimuthal $\theta$ angles.

@@

% %%%%%%%%%%%%%%%%%
% %% Description of UP |V^{a}| 3D
% %% files: 
% %% magv.sm_0.03_xb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% magv.sm_0.03_yb_12802_40-spin_scissor_0_Nc_32_incang_0-180-step5
% %% up-3d-vab.gp
% %%%%%%%%%%%%%%%%%
\begin{figure}[tb]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-1}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-1}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The maximum response zone is localized for an energy range from
    0.04\,eV to 0.12\,eV and for a polarization angle of the
    incoming beam from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-1}
\end{figure}
\begin{figure}[b]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vx-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vxb-2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ for \emph{up} structure 
    \label{fig:up-3d-vy-2}]
    {\includegraphics[width=\linewidth]{upplots/up-3d-vyb-2}}
    \caption{$|\mathcal{V}^{\mathrm{x}}|$ response for C$_{16}$H$_{8}$-up
    structure. The local maximum response zone is localized for an energy range
    from 1.95\,eV to 2.00\,eV and for a polarization angle of the incoming beam
    from 25$^{\circ}$ to 50$^{\circ}$.}
    \label{fig:up-3d-2}
\end{figure}

For the \emph{up} structure we first analyzed the energy range from 0.00\,eV to
0.16\,eV where we found the most intense response for $\mathcal{V}^{\mathrm{x}}$
and $|\mathcal{V}^{\mathrm{y}}|$. In Fig. \ref{fig:up-3d-1} we present the
$\mathcal{V}^{\mathrm{a}}$ spectra resulting from evaluate again Eq. 
\eqref{eq:va-mag} using different polarization angles $\alpha$ in Eq.  
\eqref{eq:vab} but now for the C$_{16}$H$_{8}$-up structure. We can see that the
onset of the response is when the energy of the incoming light is the same of
the gap energy.
%
From this picture we can see that for the zone between the energy range of
0.084\,eV-0.093\,eV and polarization angles between $30^{\circ}$ and
$45^{\circ}$ is the zone of the absolute maximum response for both,
$|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$. 
% 
Also there is another zone of interest, depicted in Fig. \ref{fig:up-3d-2},
where a local maximum is obtained for energies from 0.95\,eV to 0.99\,eV and
same polarization angles. From Figs. \ref{fig:up-3d-vx-2} ad 
\ref{fig:up-3d-vy-2} we have that $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}
^{\mathrm{y}}|$ reach values of 10\,Km/s and 50\,Km/s, respectively.
% %%%%%%%%%%%%%%%%
% %% Starting description of ALT |V^{a}|, components and RTP
% %% files: magv.sm_0.03_xb_14452_65-spin_scissor_0_Nc_32_incang_0-180-step5
% %%        alt-plots/alt-3d-vab.gp
% %%%%%%%%%%%%%%%%
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m1}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-1}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m1}}
    \caption{Most intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-1}
\end{figure}
\begin{figure}[t]
    \centering
    \subfigure[\ $|\mathcal{V}^{\mathrm{x}}|$ \label{fig:up-vx-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vxb-rtp-m2}}
    \\
    \subfigure[\ $|\mathcal{V}^{\mathrm{y}}|$ \label{fig:up-vy-comp-rtp-2}]
    {\includegraphics[width=\linewidth]{upplots/up-vyb-rtp-m2}}
    \caption{Intense responses of $|\mathcal{V}^{\mathrm{x}}|$ and
    $|\mathcal{V}^{\mathrm{y}}|$ and the corresponding three components for the
    \emph{up} structure. Both maxima where obtained for a polarization
    angle $\alpha=40^{\circ}$. }
    \label{fig:up-vab-comp-rtp-2}
\end{figure}
\textcolor{red}{
We found that the absolute maximum of the response is obtained when the
polarization angle is $\alpha = 40^{\circ}$. In the top frames of Figs. 
%
\ref{fig:up-vab-comp-rtp-1}  and \ref{fig:up-vab-comp-rtp-2} we present the
results for $|\mathcal{V}^{\mathrm{x}}|$ and $|\mathcal{V}^{\mathrm{y}}|$ fixing
the polarization angle to $40^{\circ}$ for the \emph{up} structure vs the photon
energy and the corresponding polar $\varphi$ and azimuthal $\theta$ angles for
the energy range from 0.0\,eV to 0.16\,eV and from 
}
